Reproducible Research in R: A Tutorial on How to Do the Same Thing More {Than Once}

### 2021-12-09 manuscript.tex
add another proof

%=================================================================
% Full title of the paper (Capitalized)
\Title{Reproducible Research in R: A Tutorial on How to Do the Same
Thing More \highlighting{Than Once}}

@@

% Authors, for the paper (add full first names)
\Author{\highlighting{Aaron Peikert~$^{1,2,*}$\href{https://orcid.org/0000-0001-7813-818X}{\orcidicon}}
, \highlighting{Caspar J. van Lissa~$^{3,4}$\href{https://orcid.org/0000-0002-0808-5024}{\orcidicon}}
 and Andreas M. Brandmaier~$^{1,5,6}$\href{https://orcid.org/0000-0001-8765-6982}{\orcidicon}}

@@

\AuthorCitation{Peikert, A.;  van Lissa, J.; Brandmaier, A.M.}
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Center for Lifespan Psychology---Max Planck Institute for Human Development, Lentzeallee 94, \mbox{14195 Berlin, Germany;} brandmaier@mpib-berlin.mpg.de\\
$^{2}$ \quad Humboldt-Universität zu Berlin, Unter den Linden 6, \mbox{10117 Berlin, Germany}
$^{3}$ \quad \hl{Department} of Methodology \& Statistics---Utrecht \hl{University}, \hl{Faculty} of Social and Behavioral Sciences
, \hl{Utrecht}, The Netherlands; C.J.vanLissa@uu.nl\\
$^{4}$ \quad Open Science Community Utrecht, \hl{Utrecht}, The Netherlands\\
$^{5}$ \quad Max Planck UCL Centre for Computational Psychiatry and Ageing Research, \mbox{\hl{Berlin, Germany, and London, UK}}\\
$^{6}$ \quad MSB Medical School Berlin, \hl{Berlin}, Germany}

@@

Scientists increasingly strive to make research data, materials, and
analysis code openly available. Sharing these digital research products
can increase scientific efficiency by enabling researchers to learn from
each other, reuse materials, and increase scientific reliability by
facilitating the review and replication of published research results.
To some extent, these potential benefits are contingent on whether these
digital research products are reproducible. Reproducibility can be
defined as the ability of anyone to obtain identical results from the
\emph{same} data with the \hl{\emph{same}}
 computer code (see~\citep{Peikert2019} \hl{for
details).}
 The credibility of empirical research results
hinges on their objectivity. Objectivity in this context means, ``in
principle it {[}the research finding{]} can be tested and understood by
anybody.'' (\citep{popperLogicScientificDiscovery2002} p.~22). Only a
reproducible result meets these requirements. Therefore, reproducibility
has long been considered integral to empirical research. Unfortunately,
despite increasing commitment to open science practices and good will,
many projects can not yet be reproduced by other research teams
\citep{obels2020}. This is because there are various challenges to
making a research project reproducible (e.g., missing software
dependencies or ambiguous documentation of the exact computational steps
taken), and there is a lack of best practices for overcoming these
challenges (but see~\citep{vanlissa2020worcs}). With technological
advancement, however, it is now possible to make all digital products
related to a research project available in a manner that enables
automatic reproduction of the research project with minimal effort.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  \highlighting{\emph{Multiple inconsistent versions of code, data, or both};}
 for
  example, the data set may have changed over time because outliers were
  removed at a later stage or an item was later recoded; or, the
  analysis code may have been modified during the writing of a paper
  because a bug was removed at some point in time. It may then be
  unclear which version of code and data was used to produce some
  reported set of results.
\item
  \highlighting{\emph{Copy-and-paste errors};} for example, results are often manually
  copied from a statistical computing language into a text processor; if
  a given analysis is re-run and results are manually updated in the
  text processor, this may inadvertently lead to inconsistencies between
  the reported result and the reproduced result.
\item
  \highlighting{\emph{Undocumented or ambiguous order of computation};} for example,
  with multiple data and code files, it may be unclear which scripts
  should be executed in what order; or, some of the computational steps
  are documented (e.g., final analysis), but other steps were conducted
  manually without documentation (e.g., executing a command manually
  rather than in a script; copy-and-pasting results from one program to
  another).
\item
  \highlighting{\emph{Ambiguous software dependencies};} for example, a given analysis
  may depend on a specific version of a specific software package, or
  rely on software that might not be available on a different computer,
  or no longer exist at all; or a different version of the same software
  may produce different results.
\end{enumerate}

@@

A second strategy is to save a so-called \texttt{Dockerfile}, which
contains only a textual description of all commands that need to be
executed to recreate the software environment. \texttt{Dockerfiles} are
tiny (the \hl{\texttt{Dockerfile}}
 (\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/Dockerfile})
for this project has a size of only 1.55~KiB). However, they rely on the
assumption that all software repositories that provide the dependent
operating systems, pieces of software, and R packages will continue to
remain accessible and provide historic software versions. For proper
archiving, we therefore recommend storing a complete image of the
software environment, in addition to the \texttt{Dockerfile}. A more
comprehensive overview of the use of containerization in research
projects is given by Wiebels and Moreau~\citep{wiebelsLeveragingContainersReproducible2021}. Note that WORCS,
which we presented elsewhere~\citep{vanlissa2020worcs} relies on the R
package \texttt{renv}~\citep{R-renv} for software management. Although
\texttt{renv} is more lightweight and easier to use than \texttt{Docker}, it is not as comprehensive because it only
takes snapshots of the R packages instead of all software used.

To summarize, the workflow by Peikert and Brandmaier~\citep{Peikert2019} requires four
components (see \highlighting{Figure~\ref{figure1})}
 dynamic document generation (using
\texttt{R\ Markdown}), version control (using \texttt{Git}), dependency
tracking (using \texttt{Make}), and software management (using
\texttt{Docker}). While \texttt{R\ Markdown} and \texttt{Git} are well
integrated into the R environment through RStudio, \texttt{Make} and
\texttt{Docker} require a level of expertise that is often beyond the
training of scholars outside the field of information technology. This
presents a considerable obstacle to the acceptance and implementation of
the workflow. To overcome this obstacle, we have developed the R package
\texttt{repro} that supports scholars in setting up, maintaining, and
reproducing research projects in R. Importantly, a reproducible research
project created with \texttt{repro} does not have the \texttt{repro}
package itself as a dependency. These projects will remain reproducible
irrespective of whether \texttt{repro} remains accessible in future.
Users do not need to have \texttt{repro} installed to reproduce a
project; in fact, they do not even need to have R installed because the
entire project can be rebuilt inside a container with R installed. In
the remainder, we will walk you through the creation of a reproducible
research project with the package~\texttt{repro}.

@@

The first step is to install the required software. We assume that you
have installed R (\citep{R-base} version 4.0.4) and RStudio
(\citep{rstudio} version 1.4) already but the tutorial will guide you in
detail through the installation of other necessary software with the
help of the R package {\texttt{repro}} 
(\url{https://github.com/aaronpeikert/repro})~\citep{R-repro}. In case you have either not installed R and RStudio or
are unsure if they are up-to-date, you might want to consult our
installation advice in the Online Supplementary Material
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md}) that covers the installation of all software
necessary for this tutorial in three steps. The
\hl{installation advice}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md}) may also help Windows users who have problems installing
\texttt{Docker}.

@@

For \texttt{Git} to recognize changes to a given file, you have to stage
and then commit these changes (this is the basic save action for a
project snapshot). One way to do this is through the visual user
interface in the RStudio \texttt{Git} pane (see \highlighting{Figure~\ref{figure2}).}
 Click on
the empty box next to the file you want to stage. A checkmark then
indicates that the file is staged. After you have staged all of the
files you want, click on the commit button, explain in the commit
message why you made those changes, and then click on commit. This
stores a snapshot of the current state of the project.

@@

We would like to note that PAC allows explicit comparison of the
preregistration and the final publication. Authors should
retrospectively summarize and justify any changes made to the
preregistered plan, e.g.~in the discussion of the \hl{final manuscript}
({In section {[}Preregistration as Code---a Tutorial{]} we
  conducted an actual PAC and summarize the changes we make to the
  preregistered code in the discussion}). During the analysis process,
authors can additionally maintain a running changelog to explain changes
in detail as they arise. Each entry in the changelog should explain the
reasoning behind the changes and link to the commit id that applied the
changes. This enables readers and reviewers to inspect individual
changes and make an informed judgment about their validity and
implications.

@@

Although researchers may use any form to preregister their planned
analyses (e.g., scripts), we suggest writing three functions for each
planned hypothesis: one to conduct the planned analysis, one to simulate
the expected data, and one to report the results. Using functions makes the
analysis more portable (i.e., it can easily be used for other datasets),
and facilitates repeated evaluation, as is the case in a simulation
study. The functions shown here do not contain executable code, but the
interested reader can find working functions in the \hl{online
supplementary materials}
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation_funs.R}) that power the example below.

@@

\begin{quote}
\hl{Navigate to}
~\url{https://zenodo.org/login/} → Log in with GitHub
\end{quote}

@@

\begin{quote}
Log into zenodo.org → Account → \hl{GitHub}~({\url{https://zenodo.org/account/settings/github/}})
\end{quote}

@@

\begin{quote}
\hl{Navigate to}
 \url{https://zenodo.org/account/settings/github/}
\end{quote}

@@

Again, we propose a preregistration format that closely resembles a
classic journal article but uses simulated data and dynamic document
generation to create a document that starts out as a preregistration and
eventually becomes the final report. The complete preregistration source
is available in the \hl{online supplementary material}
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/preregistration.Rmd}). In this section, we show code excerpts of this
preregistration (formatted in monospace) and explain the rationale
behind them.

@@

We choose the following statistical procedure because many researchers
are familiar \hl{with it}
~(The \emph{t}-test and Mann-Whitney-Wilcoxon test
  are arguably the most often used hypothesis tests (according to
 ~\citep{fagerlandTtestsNonparametricTests2012, hortonStatisticalMethodsJournal2005}
  reports that 26\% of all studies employed a \emph{t}-test and 27\% employed a
  rank-based alternative in the \emph{New England Journal of Medicine}
  in 2005). The analytical strategy presented here is, in fact,
  suboptimal in several respects (the assumption of measurement
  invariance is untested
 ~\citep{putnickMeasurementInvarianceConventions2016}, the effect size
  is underestimated in the presence of measurement error
 ~\citep{frostCorrectingRegressionDilution2000}, the effect size is
  overestimated for highly skewed distributions
 ~\citep{stonehouseRobustnessTestsCombined1998}). The interested reader
  can use the \hl{provided code for the simulation}
~\mbox{(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R})} to verify that the \emph{t}-test provides unbiased
  effect sizes but the Mann-Whitney-Wilcoxon overestimates effect sizes
  with increasing sample size and skewness.):

@@

Together with the function \texttt{simulate\_data()} (not shown here),
the function \texttt{planned\_\linebreak analysis()} can be used to justify the
planned sample size. To that end, \texttt{simulate\_data()} is
repeatedly called with increased sample sizes and the proportion of
significant results (power) is recorded. The results for such a Monte
Carlo simulation for this example are visualized in \highlighting{Figure~\ref{figure3}.}
 The code
for this power analysis can be found in the \hl{online supplementary material}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R}). The next snippet shows how we integrated the
results dynamically into the preregistration (the origin of the
R-variables \texttt{minn}, \texttt{choosen\_power}, and
\texttt{choosen\_d} is not shown).

@@

Following the recommendations outlined in this paper, we did not access
the data when we initially wrote this code. We therefore did not know
the exact format the data would have. This means that we did need to
change our preregistration after accessing the data to include i.e.,~the
recoding of gender (lines 17--22) and the items\hl{ (lines 23--26).}
We invite the reader to evaluate the changes we made to the preregistered code. Either on \hl{GitHub} (\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg...main})
  → ``Files changed'' or directly in Git with
  \texttt{git\ diff\ v0.0.1.1-prereg\ preregistration.Rmd}.) This is our
summary of what we changed:

@@

Readers can inspect and judge the changes for themselves on \hl{GitHub}
\textls[-25]{(\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main\#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b})}.

@@

The example rendered as a \hl{PDF file with real data}
(\url{https://github.com/aaronpeikert/repro-tutorial/files/7309455/preregistration.pdf}) is available in the \hl{online supplementary material}
(\url{https://github.com/aaronpeikert/repro-tutorial/releases/tag/v0.0.3.1-results}). The changes we made since preregistering it can
be inspected on this \hl{GitHub page}
(\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main\#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b}).

@@

Supplementary Materials{All materials (i.e., the source code, all figures, and the data) that are neccesary for reproducing the submitted version of this article are availible at \url{https://github.com/aaronpeikert/repro-tutorial} and archived under \url{https://doi.org/10.5281/zenodo.5724454}}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{We would like to thank Maximilian Stefan Ernst for his
contributions to the code for the simulation study. We are grateful to
Julia Delius for her helpful assistance in language and style editing.
The R package \texttt{repro} was developed as part of the \hl{first author's
master thesis}
\mbox{(\url{https://aaronpeikert.github.io/repro-thesis/})} at the Humboldt-Universität zu Berlin.}

@@

% Reference 11
\bibitem[Knuth and Levy(1994)]{knuthCWEBSystemStructured}
Knuth, D.E.; Levy, S. \emph{The CWEB System of Structured Documentation}; Addison-Wesley Longman: \hl{Boston, USA, 1994.}%MDPI: Please add the publisher’s location.

@@

% Reference 45
\bibitem[Brandmaier and Jacobucci(in press)]{brandmaier22mlsem}
Brandmaier, A.M.; Jacobucci, R. Machine-Learning Approaches to Structural Equation Modeling. In \emph{Handbook of Structural Equation Modeling}, 2nd ed.; Hoyle, R.H., Ed.; \hl{Guilford Press, New York, NY, USA}, in press.%MDPI: Please add the location of the publisher and publication year.

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Reproducible Research in R: A Tutorial on How to Do the Same
Thing More {Than Once}}

@@

% Authors, for the paper (add full first names)
\Author{{Aaron Peikert~$^{1,2,*}$\href{https://orcid.org/0000-0001-7813-818X}{\orcidicon}}
, {Caspar J. van Lissa~$^{3,4}$\href{https://orcid.org/0000-0002-0808-5024}{\orcidicon}}
 and Andreas M. Brandmaier~$^{1,5,6}$\href{https://orcid.org/0000-0001-8765-6982}{\orcidicon}}

@@

\AuthorCitation{Peikert, A.;  van Lissa, J.; Brandmaier, A.M.}
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Center for Lifespan Psychology---Max Planck Institute for Human Development, Lentzeallee 94, \mbox{14195 Berlin, Germany;} brandmaier@mpib-berlin.mpg.de\\
$^{2}$ \quad Humboldt-Universität zu Berlin, Unter den Linden 6, \mbox{10117 Berlin, Germany}

$^{3}$ \quad \hl{Department} of Methodology \& Statistics---Utrecht {University}, {Faculty} of Social and Behavioral Sciences
, Heidelberglaan 8, 3584 CS Utrecht, The Netherlands; C.J.vanLissa@uu.nl\\
$^{4}$ \quad Open Science Community Utrecht, Heidelberglaan 8, 3584 CS Utrecht, The Netherlands\\
$^{5}$ \quad Max Planck UCL Centre for Computational Psychiatry and Ageing Research, \mbox{\hl{Lentzeallee 94
14195 Berlin, Germany, and London, WC1B 5EH, UK}}\\
$^{6}$ \quad MSB Medical School Berlin, Rüdesheimer Str. 50, 14197 Berlin, Germany}

@@

Scientists increasingly strive to make research data, materials, and
analysis code openly available. Sharing these digital research products
can increase scientific efficiency by enabling researchers to learn from
each other, reuse materials, and increase scientific reliability by
facilitating the review and replication of published research results.
To some extent, these potential benefits are contingent on whether these
digital research products are reproducible. Reproducibility can be
defined as the ability of anyone to obtain identical results from the
\emph{same} data with the {\emph{same}}
 computer code (see~\citep{Peikert2019} {for
details).}
 The credibility of empirical research results
hinges on their objectivity. Objectivity in this context means, ``in
principle it {[}the research finding{]} can be tested and understood by
anybody.'' (\citep{popperLogicScientificDiscovery2002} p.~22). Only a
reproducible result meets these requirements. Therefore, reproducibility
has long been considered integral to empirical research. Unfortunately,
despite increasing commitment to open science practices and good will,
many projects can not yet be reproduced by other research teams
\citep{obels2020}. This is because there are various challenges to
making a research project reproducible (e.g., missing software
dependencies or ambiguous documentation of the exact computational steps
taken), and there is a lack of best practices for overcoming these
challenges (but see~\citep{vanlissa2020worcs}). With technological
advancement, however, it is now possible to make all digital products
related to a research project available in a manner that enables
automatic reproduction of the research project with minimal effort.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  {\emph{Multiple inconsistent versions of code, data, or both};}
 for
  example, the data set may have changed over time because outliers were
  removed at a later stage or an item was later recoded; or, the
  analysis code may have been modified during the writing of a paper
  because a bug was removed at some point in time. It may then be
  unclear which version of code and data was used to produce some
  reported set of results.
\item
  {\emph{Copy-and-paste errors};} for example, results are often manually
  copied from a statistical computing language into a text processor; if
  a given analysis is re-run and results are manually updated in the
  text processor, this may inadvertently lead to inconsistencies between
  the reported result and the reproduced result.
\item
  {\emph{Undocumented or ambiguous order of computation};} for example,
  with multiple data and code files, it may be unclear which scripts
  should be executed in what order; or, some of the computational steps
  are documented (e.g., final analysis), but other steps were conducted
  manually without documentation (e.g., executing a command manually
  rather than in a script; copy-and-pasting results from one program to
  another).
\item
  {\emph{Ambiguous software dependencies};} for example, a given analysis
  may depend on a specific version of a specific software package, or
  rely on software that might not be available on a different computer,
  or no longer exist at all; or a different version of the same software
  may produce different results.
\end{enumerate}

@@

A second strategy is to save a so-called \texttt{Dockerfile}, which
contains only a textual description of all commands that need to be
executed to recreate the software environment. \texttt{Dockerfiles} are
tiny (the {\texttt{Dockerfile}}
 (\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/Dockerfile} accessed on 11 October 2021)
for this project has a size of only 1.55~KiB). However, they rely on the
assumption that all software repositories that provide the dependent
operating systems, pieces of software, and R packages will continue to
remain accessible and provide historic software versions. For proper
archiving, we therefore recommend storing a complete image of the
software environment, in addition to the \texttt{Dockerfile}. A more
comprehensive overview of the use of containerization in research
projects is given by Wiebels and Moreau~\citep{wiebelsLeveragingContainersReproducible2021}. Note that WORCS,
which we presented elsewhere~\citep{vanlissa2020worcs} relies on the R
package \texttt{renv}~\citep{R-renv} for software management. Although
\texttt{renv} is more lightweight and easier to use than \texttt{Docker}, it is not as comprehensive because it only
takes snapshots of the R packages instead of all software used.

To summarize, the workflow by Peikert and Brandmaier~\citep{Peikert2019} requires four
components (see {Figure~\ref{figure1})}
 dynamic document generation (using
\texttt{R\ Markdown}), version control (using \texttt{Git}), dependency
tracking (using \texttt{Make}), and software management (using
\texttt{Docker}). While \texttt{R\ Markdown} and \texttt{Git} are well
integrated into the R environment through RStudio, \texttt{Make} and
\texttt{Docker} require a level of expertise that is often beyond the
training of scholars outside the field of information technology. This
presents a considerable obstacle to the acceptance and implementation of
the workflow. To overcome this obstacle, we have developed the R package
\texttt{repro} that supports scholars in setting up, maintaining, and
reproducing research projects in R. Importantly, a reproducible research
project created with \texttt{repro} does not have the \texttt{repro}
package itself as a dependency. These projects will remain reproducible
irrespective of whether \texttt{repro} remains accessible in future.
Users do not need to have \texttt{repro} installed to reproduce a
project; in fact, they do not even need to have R installed because the
entire project can be rebuilt inside a container with R installed. In
the remainder, we will walk you through the creation of a reproducible
research project with the package~\texttt{repro}.

@@

The first step is to install the required software. We assume that you
have installed R (\citep{R-base} version 4.0.4) and RStudio
(\citep{rstudio} version 1.4) already but the tutorial will guide you in
detail through the installation of other necessary software with the
help of the R package {\texttt{repro}} 
(\url{https://github.com/aaronpeikert/repro})~\citep{R-repro}. In case you have either not installed R and RStudio or
are unsure if they are up-to-date, you might want to consult our
installation advice in the Online Supplementary Material
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md}) that covers the installation of all software
necessary for this tutorial in three steps. The
{installation advice}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md} accessed on 11 October 2021) may also help Windows users who have problems installing
\texttt{Docker}.

@@

For \texttt{Git} to recognize changes to a given file, you have to stage
and then commit these changes (this is the basic save action for a
project snapshot). One way to do this is through the visual user
interface in the RStudio \texttt{Git} pane (see {Figure~\ref{figure2}).}
 Click on
the empty box next to the file you want to stage. A checkmark then
indicates that the file is staged. After you have staged all of the
files you want, click on the commit button, explain in the commit
message why you made those changes, and then click on commit. This
stores a snapshot of the current state of the project.

@@

We would like to note that PAC allows explicit comparison of the
preregistration and the final publication. Authors should
retrospectively summarize and justify any changes made to the
preregistered plan, e.g.~in the discussion of the {final manuscript}
({In section {[}Preregistration as Code---a Tutorial{]} we
  conducted an actual PAC and summarize the changes we make to the
  preregistered code in the discussion}). During the analysis process,
authors can additionally maintain a running changelog to explain changes
in detail as they arise. Each entry in the changelog should explain the
reasoning behind the changes and link to the commit id that applied the
changes. This enables readers and reviewers to inspect individual
changes and make an informed judgment about their validity and
implications.

@@

Although researchers may use any form to preregister their planned
analyses (e.g., scripts), we suggest writing three functions for each
planned hypothesis: one to conduct the planned analysis, one to simulate
the expected data, and one to report the results. Using functions makes the
analysis more portable (i.e., it can easily be used for other datasets),
and facilitates repeated evaluation, as is the case in a simulation
study. The functions shown here do not contain executable code, but the
interested reader can find working functions in the {online
supplementary materials}
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation_funs.R} accessed on 11 October 2021) that power the example below.

@@

\begin{quote}
{Navigate to}
~\url{https://zenodo.org/login/ accessed on 11 October 2021} → Log in with GitHub
\end{quote}

@@

\begin{quote}
Log into zenodo.org → Account → {GitHub}~({\url{https://zenodo.org/account/settings/github/}})
\end{quote}

@@

\begin{quote}
{Navigate to}
 \url{https://zenodo.org/account/settings/github/}
\end{quote}

@@

Again, we propose a preregistration format that closely resembles a
classic journal article but uses simulated data and dynamic document
generation to create a document that starts out as a preregistration and
eventually becomes the final report. The complete preregistration source
is available in the {online supplementary material}
~(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/preregistration.Rmd} accessed on 11 October 2021). In this section, we show code excerpts of this
preregistration (formatted in monospace) and explain the rationale
behind them.

@@

We choose the following statistical procedure because many researchers
are familiar {with it}
~(The \emph{t}-test and Mann-Whitney-Wilcoxon test
  are arguably the most often used hypothesis tests (according to
 ~\citep{fagerlandTtestsNonparametricTests2012, hortonStatisticalMethodsJournal2005}
  reports that 26\% of all studies employed a \emph{t}-test and 27\% employed a
  rank-based alternative in the \emph{New England Journal of Medicine}
  in 2005). The analytical strategy presented here is, in fact,
  suboptimal in several respects (the assumption of measurement
  invariance is untested
 ~\citep{putnickMeasurementInvarianceConventions2016}, the effect size
  is underestimated in the presence of measurement error
 ~\citep{frostCorrectingRegressionDilution2000}, the effect size is
  overestimated for highly skewed distributions
 ~\citep{stonehouseRobustnessTestsCombined1998}). The interested reader
  can use the {provided code for the simulation}
~\mbox{(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R})} to verify that the \emph{t}-test provides unbiased
  effect sizes but the Mann-Whitney-Wilcoxon overestimates effect sizes
  with increasing sample size and skewness.):

@@

Together with the function \texttt{simulate\_data()} (not shown here),
the function \texttt{planned\_\linebreak analysis()} can be used to justify the
planned sample size. To that end, \texttt{simulate\_data()} is
repeatedly called with increased sample sizes and the proportion of
significant results (power) is recorded. The results for such a Monte
Carlo simulation for this example are visualized in {Figure~\ref{figure3}.}
 The code
for this power analysis can be found in the {online supplementary material}
(\url{https://github.com/aaronpeikert/repro-tutorial/blob/main/R/simulation.R} accessed on 11 October 2021). The next snippet shows how we integrated the
results dynamically into the preregistration (the origin of the
R-variables \texttt{minn}, \texttt{choosen\_power}, and
\texttt{choosen\_d} is not shown).

@@

Following the recommendations outlined in this paper, we did not access
the data when we initially wrote this code. We therefore did not know
the exact format the data would have. This means that we did need to
change our preregistration after accessing the data to include i.e.,~the
recoding of gender (lines 17--22) and the items{ (lines 23--26).}
We invite the reader to evaluate the changes we made to the preregistered code. Either on {GitHub} (\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg...main} accessed on 11 October 2021)
  → ``Files changed'' or directly in Git with
  \texttt{git\ diff\ v0.0.1.1-prereg\ preregistration.Rmd}.) This is our
summary of what we changed:

@@

Readers can inspect and judge the changes for themselves on {GitHub}
\textls[-25]{(\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main\#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b})}.

@@

The example rendered as a {PDF file with real data}
(\url{https://github.com/aaronpeikert/repro-tutorial/files/7309455/preregistration.pdf} accessed on 11 October 2021) is available in the {online supplementary material}
(\url{https://github.com/aaronpeikert/repro-tutorial/releases/tag/v0.0.3.1-results} accessed on 11 October 2021). The changes we made since preregistering it can
be inspected on this {GitHub page}
(\url{https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main\#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b} accessed on 11 October 2021).

@@

Supplementary Materials {All materials (i.e., the source code, all figures, and the data) that are neccesary for reproducing the submitted version of this article are availible at \url{https://github.com/aaronpeikert/repro-tutorial} and archived under \url{https://doi.org/10.5281/zenodo.5724454}}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{We would like to thank Maximilian Stefan Ernst for his
contributions to the code for the simulation study. We are grateful to
Julia Delius for her helpful assistance in language and style editing.
The R package \texttt{repro} was developed as part of the {first author's
master thesis}
\mbox{(\url{https://aaronpeikert.github.io/repro-thesis/} accessed on 11 October 2021)} at the Humboldt-Universität zu Berlin.}

@@

% Reference 11
\bibitem[Knuth and Levy(1994)]{knuthCWEBSystemStructured}
Knuth, D.E.; Levy, S. \emph{The CWEB System of Structured Documentation}; Addison-Wesley Longman: \hl{Boston, USA, 1994.}

@@

% Reference 45
\bibitem[Brandmaier and Jacobucci(in press)]{brandmaier22mlsem}
Brandmaier, A.M.; Jacobucci, R. Machine-Learning Approaches to Structural Equation Modeling. In \emph{Handbook of Structural Equation Modeling}, 2nd ed.; Hoyle, R.H., Ed.; \hl{Guilford Press, New York, NY, USA}, in press.
